# Results

```{r}
library(dplyr)
library(lubridate)
library(ggplot2)
library(tidyverse)
library(GGally)
library(gridExtra)
library(patchwork)
library(ggalluvial)
library(redav)
```

```{r}
# import the data
data <- read.csv("~/Desktop/Health expenditure and financing.csv")
data <- data[, c(1, 3, 5, 7, 9, 11, 13, 15, 19)]
country <- c("BRA", "CAN", "CHL", "DEU", "FRA", "GBR", "ISL", "MEX", "POL", "RUS", "TUR", "USA")
data <- data %>%
  filter(LOCATION %in% country) %>%
  mutate(TYPE = ifelse(LOCATION %in% c("BRA", "CHL", "MEX", "POL", "RUS", "TUR"), "DEVELOPING", "DEVELOPED")) %>%
  filter(HF == "HFTOT")
```

## Total health expenditure

### Trends of total health expenditure in various countries

```{r fig.align = 'center', fig.width = 10}
# filter the data
data1 <- data %>%
  filter(HC == "HCTOT", HP == "HPTOT", MEASURE == "MLLNCU", TIME %in% c(2010:2019)) %>%
  mutate(Time = dmy(paste(1, 1, TIME)))
# standardize the value
data1.1  = data1 %>%
  mutate(Value_std = ifelse(TIME == 2010, 1, 0))
year <- c(2011:2019)
for (i in 1:length(country)){
  for (j in 1:length(year)){
    data1.1[data1.1$LOCATION == country[i] & data1.1$TIME == year[j],]$Value_std <- 1 + 
      (data1.1[data1.1$LOCATION == country[i] & data1.1$TIME == year[j],]$Value -
         data1.1[data1.1$LOCATION == country[i] & data1.1$TIME == 2010,]$Value)/
      data1.1[data1.1$LOCATION == country[i] & data1.1$TIME == 2010,]$Value
  }
}
# plot the time series
ggplot(data1.1, aes(Time, Value_std)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.5, vjust = 0.5))+
  facet_wrap(LOCATION ~.)
```

From the time series plot above, we could find that total health expenditure of all countries kept increasing. After standardization, we can see that Brazil, Chili, Russia and Turkey had significant growth trends, and they were all developing countries; while Canada, Germany, France, the United Kingdom and the United States had relatively slow growth, and all of them were developed countries. To be specific, compared with developing countries, health expenditure in most developed countries were growing stably and slowly.


### Trends of total health expenditure per capita in various countries

```{r fig.align = 'center'}
# filter the data
data2 <- data %>% 
  filter(HC == "HCTOT", HP == "HPTOT", MEASURE == "PPPPER", TIME %in% c(2010:2019)) %>%
  select(LOCATION, TIME, Value, TYPE) %>%
  pivot_wider(names_from = TIME, values_from = Value) %>%
  as_tibble()
# draw the parallel coordinate plot
ggparcoord(data2, columns = c(4:12), scale = "globalminmax", groupColumn = "TYPE") +
  geom_vline(xintercept = 2:8, color = "dark grey") +
  geom_text(x = 9.2, y = data2[data2$LOCATION == "USA",]$`2019` - 500, label = "USA", color = "black")
```

From the parallel coordinate plot above, we could find that total health expenditure per capita of all countries showed an upward trend year by year. What's more, the expenditure per capita of developed countries was much higher than that of developing countries, and developed countries had more obvious growing trends over year. To be specific, the health expenditure per capita of the United States was much higher than other countries from 2011 to 2019, which also grew more quickly from 2014 to 2019.


### Trends in the ratio of total health expenditure to GDP in various countries

```{r fig.align = 'center', fig.height = 8, fig.width = 12}
# filter the data
data3 = data %>% 
  filter(HC == "HCTOT", HP == "HPTOT", MEASURE == "PARPIB", TIME %in% c(2010:2019)) 
data3$TIME <- as.character(data3$TIME)
data3$LOCATION <- factor(data3$LOCATION, levels = c("USA", "FRA", "DEU", "CAN", "GBR", "ISL",
                                                    "BRA", "CHL", "POL", "MEX", "RUS", "TUR"))
# draw the cleveland dot plot
g1 <- data3 %>%
  filter(TYPE == "DEVELOPED") %>%
  ggplot(aes(x = Value, y = TIME)) +
  geom_point() +
  facet_grid(LOCATION ~ TYPE)
g2 <- data3 %>%
  filter(TYPE == "DEVELOPING") %>%
  ggplot(aes(x = Value, y = TIME)) +
  geom_point() +
  facet_grid(LOCATION ~ TYPE) +
  labs(y = "")
grid.arrange(g1, g2, nrow = 1)
```

From the cleveland dot plot above, we could find that the ratio of total health expenditure to GDP of developed countries was much higher than that of developing countries. To be specific, the ratio of the United States was much higher than that of other countries, which exceeded 15% while others all lower than 12%.  
As for developed countries on the left, all six countries showed a fluctuating trend, increasing and decreasing alternatively around one certain value.  
As for developing countries on the right, six countries varied a lot. Brazil, Chili and Russia showed a growing trend, and Chili increased most significantly, Poland and Mexico showed a fluctuating trend, while Turkey showed a descending trend.

## Expenditure on different medical products and services

### Expenditure on different medical products and services in different countries in 2019

```{r fig.align = 'center'}
# filter the data
data4 <- data %>%
  filter(HC != "HCTOT", HP == "HPTOT", MEASURE == "PARCUR", TIME == "2019") %>%
  select(LOCATION, HC, Value)
head(data4)
# draw the heatmap
ggplot(data4, aes(x = LOCATION, y = HC)) + 
  geom_tile(aes(fill = Value), color = "white") + 
  coord_fixed() +
  scale_fill_distiller(palette = "Reds", limits = c(0, 50), direction = 1) +
  theme_classic()
```

From the heatmap above, we could find that `HC11HC21` and `HC13HC23` have the most prominent colors, followed by `HC5` and `HC3`, while `HC4`, `HC7`, `HC6` and `HC0` have relative light colors, which means that inpatient and outpatient curative and rehabilitative care takes dominant position in health expenditure, followed by medical goods and long term care, and the proportions of the other fours, ancillary services, governance and health system and financing administration, preventive care and other health care services are not much.
Moreover, as for inpatient curative and rehabilitative care, Russia expended the most; as for outpatient curative and rehabilitative care, the United states was higher than others; as for long term care, Canada, Germany, France, the United Kingdom and Iceland spent more than the other countries, and they are all developed countries.


### Expenditure on different medical products and services in developed and developing countries in 2019

```{r fig.align = 'center', fig.width = 10}
# filter the data for developed countries
data5.1 <- data4 %>%
  filter(LOCATION %in% c("FRA", "GBR", "USA"))
# filter the data for developing countries
data5.2 <- data4 %>%
  filter(LOCATION %in% c("BRA", "POL", "RUS"))
# draw the stacked barchart
g1 <- ggplot(data5.1, aes(x = LOCATION, y = Value, fill = HC)) + 
  geom_bar(position = "fill", stat = "identity") +
  scale_fill_brewer(palette = "RdYlBu") +
  theme(legend.position = "none")
g2 <- ggplot(data5.2, aes(x = LOCATION, y = Value, fill = HC)) + 
  geom_bar(position ="fill", stat = "identity") +
  scale_fill_brewer(palette = "RdYlBu") +
  labs(y = "")
g1 + g2
```

From the stacked bar charts above, we could find that compared to developed countries, developing countries expended more on inpatient curative and rehabilitative care (`HC11HC21`), ancillary services (`HC4`) and medical goods (`HC5`), less on long term care (`HC3`) and governance and health system and financing administration (`HC7`).  
From the left plot of developed countries, the United States spent more on outpatient curative and rehabilitative care (`HC13HC23`), less on inpatient curative and rehabilitative care and long term care than France and the the United Kingdom.  
From the right plot of developing countries, Russia spent more on inpatient curative and rehabilitative care, less on outpatient curative and rehabilitative care and long term care than Brazil and Poland.


### Expenditure trend of different medical products and services in USA and Poland

```{r fig.align = 'center', fig.width = 10}
# filter the data for USA and Poland
data6 <- data %>%
  filter(HC != "HCTOT", HP == "HPTOT", MEASURE == "PARCUR", LOCATION %in% c("USA", "POL")) %>%
  select(LOCATION, TIME, HC, Value) %>%
  mutate(Time = dmy(paste(1, 1, TIME)))
data6$LOCATION <- factor(data6$LOCATION, levels = c("USA", "POL"))
# draw the multiple line chart
ggplot(data6, aes(x = Time, y = Value, color = HC)) +
  geom_line() +
  facet_wrap(~LOCATION)
```

From the multiple line chart above, we could find that from 2010 to 2019, the top three health expenditures on different medical products and services of both the United States and Poland were inpatient curative and rehabilitative care (`HC11HC21`), outpatient curative and rehabilitative care (`HC13HC23`) and medical goods (`HC5`).  
As for the United States, the expenditure on different medical products and services did not change obviously. Moreover, the proportion of outpatient curative and rehabilitative care exceeded 40% with an increasing trend, which was significantly higher than that of other functions.  
As for Poland, except for the top three health expenditures mentioned above, the expenses for other functions did not change a lot. What's more, from 2014 to 2016, inpatient curative first decreased obviously and then returned to the initial level, while outpatient curative first increased significantly and then decreased slightly. Both changes were in the same time period, which indicated that the demand for inpatient curative converted to outpatient curative during this time.


## Expenditure on different organizations and actors that deliver health care goods and services

### Expenditure on different providers in different countries in 2010 and 2019

```{r fig.align = 'center', fig.height = 8, fig.width = 10}
# filter the data
data7 <- data %>% 
  filter(HC == "HCTOT", HP %in% c("HP1", "HP2", "HP3", "HP5", "HP6", "HP7"), MEASURE == "PARCUR",
         LOCATION %in% c("USA", "TUR", "MEX", "POL", "ISL", "DEU", "FRA", "CAN"), TIME %in% c(2010, 2019)) 
data7$TIME <- as.character(data7$TIME)
# draw the grouped bar chart
ggplot(data7, aes(x = Value, y = HP, fill = TIME)) +
  geom_bar(position = "dodge", stat = "identity")+
  facet_wrap(LOCATION~., ncol = 2) +
  scale_fill_discrete(breaks = c("2019", "2010"))
```

From the grouped bar charts above, we could find that compared to 2010, the ratio of each provider’s medical expenditure to total health expenditure in 2019 did not change much, but the proportion of expenditure among each provider varied. To be specific, health expenditures of most countries were concentrated on hospitals (`HP1`), providers of ambulatory health care (`HP3`) and retailers and other providers of medical goods (`HP5`), but little on residential long-term care facilities (`HP2`), providers of preventive care (`HP6`) and providers of health care system administration and financing (`HP7`).  
Now, we focus on Turkey. In Turkey, hospitals accounted for as high as 50% in 2019 with an obvious growth compared to 2010, while the proportions of ambulatory health care and providers of medical goods decreased from 2010 to 2019, which indicated that as time went, people in this country tended to go to the hospital for treatment rather than go to institutions that provide medical care services.


### Trend of the expenditure on hospitals in different countries

```{r fig.align = 'center'}
# filter the data
data8 <- data %>% 
  filter(HC == "HCTOT", HP == "HP1", MEASURE == "PARCUR", TIME %in% c(2014:2019))
# calculate the changing rate each year
country2 <- c("CAN", "DEU", "FRA", "GBR", "ISL", "MEX", "POL", "RUS", "TUR", "USA")
year2 <- c(2014:2019)
data8$Rate <- 0
for (i in 1:10){
  for (j in 2:6){
    data8[data8$TIME == year2[j] & data8$LOCATION == country2[i],]$Rate =
      (data8[data8$TIME == year2[j] & data8$LOCATION == country2[i],]$Value -
         data8[data8$TIME == year2[j - 1] & data8$LOCATION == country2[i],]$Value)/
      data8[data8$TIME == year2[j - 1] & data8$LOCATION == country2[i],]$Value
  }
}
data8 <- data8[data8$TIME != 2014,]
# label the changing rate
data8 = data8 %>% 
  mutate(Level = cut(Rate, breaks = c(min(data8$Rate), 0, max(data8$Rate)),
                     labels = c("NEGATIVE", "POSITIVE"), include.lowest = TRUE)) %>%
  select(LOCATION, Value, Rate, Level, TIME)
data8$Time = as.character(data8$TIME)
# draw the alluvial diagram
ggplot(data8, mapping = aes(x = TIME, y = 1, stratum = Level, alluvium = LOCATION))+
  geom_alluvium(aes(fill = LOCATION), color = "grey40") + 
  geom_stratum(width = 0.5) + 
  geom_text(stat = "stratum", aes(label = after_stat(stratum)), size = 1.5) +
  scale_y_reverse(breaks = NULL) +
  labs(x = "Time", y = "Level")
```

From the alluvial diagram above, we could find that from 2015 to 2019, the expenditure percentage on hospital of Poland kept growing, while that of Germany kept descending; Countries such as Iceland, France, the United Kingdom and Turkey first increased and then decreased, it was worth noting that three of four are developed countries; the remaining four countries, i.e., Russia, Mexico, the United States and Canada did not have an obvious trend, their changing rates constantly varied in positive and negative directions.  
As for time dimension, we could find that from 2015 to 2016, the expenditure percentage on hospital of most countries kept increasing or decreasing, from 2016 to 2017 and 2018 to 2019, there was no change in growth or decline trend for more than half of the countries; from 2017 to 2018, half of the countries changed, which was the most chaotic time period.


### Correlation between different providers

```{r fig.align = 'center'}
# filter the data
data9 <- data %>% 
  filter(HC == "HCTOT", HP %in% c("HP1", "HP2", "HP3", "HP5", "HP6", "HP7"), MEASURE == "PARCUR", TIME == 2019) %>%
  select(LOCATION, HP, Value) %>%
  pivot_wider(names_from = HP, values_from = Value)
data9[4,6] <- 0
# draw the biplot
draw_biplot(data9, fix_sign = TRUE)
```

From the biplot above, we could find that `HP3` (providers of ambulatory health care) and `HP7` (providers of health care system administration and financing), `HP5` (retailers and other providers of medical goods) and `HP6` (providers of preventive care) form small angles, which means that the expenditure percentage of ambulatory health care and health care system administration and financing, medical goods and preventive care are highly correlated. What's more, the angles between `HP1` (hospitals), `HP2` (residential long-term care facilities), `HP3` and `HP7`, `HP5` and `HP6` are nearly 90 degrees, which means that apart from the four previously mentioned providers, there is basically no relationship between the expenditure percentages of other providers.